TRITON: Globally Consistent Sim-to-Real Transfer

### 2022-06-03 CORL/example.tex
Updated the main document

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=200pt]{frame_inconsistency_diagram.pdf}
	\end{center}
	\caption{
		Each row of images is a different random placement of object in a scene.
		Each column is a different image translation algorithm.
		The same cube is marked with the same color outline across all photos.
		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		CUT and CycleGan are not consistent, while TRITON is.
		TODO: Update the images in this to have the latest training iteration...
		}
	\label{fig:main_diagram}
\end{figure}

@@

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{main_diagram.pdf}
	\end{center}
	\caption{
		This is the main diagram for the paper.
		TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		TODO: Use variables instead of 3,4 
		TODO: Make the text larger and easier to read
		TODO: Simplify the diagram?
		}
	\label{fig:main_diagram}
\end{figure}

>>>>

This algorithm unlocks a new capability: learning textures to match photos for given 3d models without supervision.

@@

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=200pt]{dataset_explanation.pdf}
	\end{center}
	\caption{
		Compatiable datasets have two sets of images: a set of UVL scenes and a set of photographs.
		TRITON is a sim-to-real image translation algorithm, taking in synthetic UVL scenes and aiming to create realistic fake photographs. 
		Being an unsupervised algorithm, there are no correspondences between synthetic and real images.
		In this dataset, three alphabet cubes are moved around the table. 
		The synthetic and real cameras have the same position and field of view.
		There are many more UVL scenes than photos, because synthetic scenes can be generated automatically whereas photos require real-world labor.
		}
	\label{fig:dataset_explanation}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{main_diagram_condensed.pdf}
	\end{center}
	\caption{
		This is the main diagram for the paper. $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		TODO: Use variables instead of 3,4
		TODO: Make the text larger and easier to read
		TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{unprojection_consistency_loss.pdf}
	\end{center}
	\caption{
		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $\u_{1...R,1...L}$, 
		\pi
	}
	\label{fig:unprojection_consistency_loss}
\end{figure}

\section{Citations}
\label{sec:citations}
\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{frame_inconsistency_diagram.pdf}
	\end{center}

	% Each outline color corresponds to the same cube.
	% The same cubes are marked with the same colored outlines across all photos.
	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.

	\caption{
		Each row of images is a different random placement of object in a scene.
		Each column is a different image translation algorithm.
		The same cube is marked with the same color outline across all photos.
		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		CUT and CycleGan are not consistent, while TRITON is.
		TODO: Update the images in this to have the latest training iteration...
		}
	\label{fig:frame_inconsistency_diagram}
\end{figure}

\section{Limitaions}
\label{sec:Limitations}

Can't handle transparent objects. 
Limited number of objects can be learned at once before supervision is nessecary with color loss (but there are workarounds).
Takes a long time to train.
